#Aim: To learn how to create an algorithm that can find a polygon's centroid
#Prerec- Create the polygon
#This is done using poly_mat and matrices representing the polygons vertices 
#This code will not work for non-convex polygons 
```{r} 
 #This code confirms that the object was created
if(!exists("poly_mat")) {
  message("No poly_mat object provided, creating object representing a 9 by 9 square")
 #This code creates the polygon
  poly_mat = cbind(
    x = c(0, 0, 9, 9, 0),
    y = c(0, 9, 9, 0, 0)
  )}
```
#Create sub triangles 
```{r}
Origin = poly_mat[1,] #Creates the origin point
#Generalized function for creating triangles from all verticies
i = 2:(nrow(poly_mat) - 2)
T_all = lapply(i, function(x) { 
  rbind(Origin, poly_mat[x:(x+1), ], Origin)
  })
```
#Calculate triangle centroids
```{r}
C_list = lapply(T_all,  function(x) (x[1, ] + x[2, ] + x[3, ]) / 3) #finds the centroid for each column in T_all (Each polygon)
C = do.call(rbind, C_list)
```
#Calculate triangle areas
```{r}
#vapply produces a single value (area) for every x in function(x)
A = vapply(T_all, function(x) { 
   abs(x[1, 1] * (x[2, 2] - x[3, 2]) +
        x[2, 1] * (x[3, 2] - x[1, 2]) +
        x[3, 1] * (x[1, 2] - x[2, 2]) ) / 2
}, FUN.VALUE = double(1))
```
#Calculate area weighted centroid average (which would be the centroid of the whole polygon)
```{r}
poly_area = sum(A)
print(paste0("The area is:", poly_area))
poly_centroid = c(weighted.mean(C[ , 1], A), weighted.mean(C[ , 2], A))
```
#Output final results
```{r}
print(paste0("The coordinates of the centroid are:", round(poly_centroid[1], 2), ",",
round(poly_centroid[2], 2)))
```
